Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-06-08 vignette/191115_PMMB_DataWrangling_PM.Rmd
Tidy up some errant lines

#dim(Fogerty_17)   # 162 rows , 43 Columns

@@

# I have comment out this code because it does not replace the control plots properly
# insert new calculations into data
# PM_MB_means <-   replace_data(template_data = PM_MB_means, 
#                             new_data = Fogerty_17_m, 
#                             new_data_column = "AUDPC_m", 
#                             ignore_columns = c(5:8,10:16,29:46))
#

@@

# Calculate AUDPC
Well_18_dat <- cbind(Well_18_dat,
                          AUDPC = apply(data.frame(zero = 0,
                                                   Well_18[,c("IR.23-3-18","IR.5-4-18", "IR.11-4-18", "IR.18-4-18","IR.26-4-18","IR.2-5-18")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c((Well_18_dat$first_sign_disease[1]-7)-
                                                     Well_18_dat$planting_date[1],
                                                  38,51 ,57,64,72,78)
                                        ),
                     AUDPS = apply(data.frame(zero = 0,
                                                   Well_18[,c("IR.23-3-18","IR.5-4-18", "IR.11-4-18", "IR.18-4-18","IR.26-4-18","IR.2-5-18")]-1),
                                        1, 
                                        FUN = audps, 
                                        dates = c((Well_18_dat$first_sign_disease[1]-7)-
                                                     Well_18_dat$planting_date[1],
                                                  38,51 ,57,64,72,78)
                                        )
                          )
Well_18_dat$total_fungicide
```

@@

source(here("R/replace_data.R"))

@@

write.csv(PM_MB_means, file = here("cache/PM_MB_updated.csv"), row.names = FALSE)
getwd()
```

>>>>

@@

# I have comment out this code because it does not replace the control plots properly as there is nothing to separate them from each other
# insert new calculations into data
#PM_MB_means <-   
   # replace_data(template_data = PM_MB_means,
   #                          new_data = Fogerty_17_m,
   #                          new_data_column = "AUDPC_m",
   #                          ignore_columns = c(5:8,10:16,29:46),
   #                          subset_factor = "mung1617/02")

@@

# Calculate AUDPC
Well_18_dat <- cbind(Well_18_dat,
                          AUDPC = apply(data.frame(zero = 0,
                                                   Well_18[,c("IR.23-3-18","IR.5-4-18", "IR.11-4-18", "IR.18-4-18","IR.26-4-18","IR.2-5-18")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c((Well_18_dat$first_sign_disease[1]-7)-
                                                     Well_18_dat$planting_date[1],
                                                  38,51 ,57,64,72,78)
                                        ),
                     AUDPS = apply(data.frame(zero = 0,
                                                   Well_18[,c("IR.23-3-18","IR.5-4-18", "IR.11-4-18", "IR.18-4-18","IR.26-4-18","IR.2-5-18")]-1),
                                        1, 
                                        FUN = audps, 
                                        dates = c((Well_18_dat$first_sign_disease[1]-7)-
                                                     Well_18_dat$planting_date[1],
                                                  38,51 ,57,64,72,78)
                                        )
                          )

@@

@@

write.csv(PM_MB_means, file = here("cache/PM_MB_updated.csv"), row.names = FALSE)
